\documentclass[]{article}
\usepackage{setspace}
\usepackage[acronym]{glossaries}
\doublespacing
\input{../../definitions.tex}
\newcommand{\theweek}{1}
%glossary items
\newglossaryentry{lc}{name=LC, description={letter of credit}}
\newglossaryentry{bl}{name=BL, description={bill of lading}}
\newglossaryentry{rtw}{name=RTW, description={Return to Work}}
\newglossaryentry{poet}{name=PoET,description={Proof of Elapsed-Time}}
\newglossaryentry{pow}{name=PoW,description={Proof of Work}}
\makeglossaries
% makeindex -s notes.ist -o notes.gls notes.glo
\begin{document}
\title{\moduleCode\ Lecture Notes for Learning Week \theweek }
\author{\moduleLeader}
\maketitle

%\glsadd{bc}
%\glsadd{rtw}
%\glsadd{jit}
%\glsadd{iot}
\glsadd{l/c} Letter of credit
\glsaddall
\printglossaries

Blockchain applications and data modelling.

\begin{description}
	\item [6] Communication and Interoperability. Communicate securely across an organisation on an open network. Interoperability, OS agnostic and web-based.
	\item[10] This is not  a flowchart?	
	\item[10] look at flowchart in NIST? print 53 of yaga (NIST review)
	\item[13] Separation of concerns: chunk. Separate problem domain so that each part has its own, and only one, concern. A concern is a set of information that affects software. Normally, in OO-design concerns are separated into objects.
	\item[13] colour is an asset of car? In manufacturing and selling colour could be an important asset, however, in taxis or car hire, it becomes a less important asset and more of an attribute. The concern is not high enough.
	\item[20] L/C letter of credit
		

\end{description}

\end{document}
